---
chapter: "graphics"
author: "Daniel Kaplan"
date: 2018-11-29 
version: 0.1
topics: [violin, jitter, density]
id: cheetah-hit-plate 
---

```{r cheetah-hit-plate-setup, include = FALSE}
library(NHANES)
library(dplyr)
library(mosaic)
library(mosaicData)
library(ggformula)
```

TITLE GOES HERE: The graph below is a violin plot. Using a pencil and your intuition, add a few dozen dots to the graphic as they would appear in a data layer superimposed on the violin layer. The dots should be jittered and be consistent with the shape of the violins.

```{r cheetah-hit-plate-1, echo = FALSE}
NHANES %>% 
  dplyr::select(Poverty, HomeOwn) %>%
  na.omit() %>%
  filter(HomeOwn != "Other", Poverty != 5) %>%
  gf_violin(Poverty ~ HomeOwn, fill = "gray", alpha = 0.4, color = NA ) %>%
    gf_labs(y = "Income (1 = poverty level)", x = "Housing status")
```


<!--answer-start-->

Where the violin is wider, there is a greater concentration of dots. In a jittered plot, the exact horizontal position of the dots has no significance.

```{r cheetah-hit-plate-answer, echo = FALSE}
NHANES %>% 
  dplyr::select(Poverty, HomeOwn) %>%
  na.omit() %>%
  filter(HomeOwn != "Other", Poverty != 5) %>%
  gf_violin(Poverty ~ HomeOwn, fill = "gray", alpha = 0.4, color = NA ) %>%
    gf_labs(y = "Income (1 = poverty level)", x = "Housing status") %>%
    gf_jitter(data = . %>% sample_n(size = 200), width = 0.2)
```
<!--answer-end-->
