---
chapter: "graphics"
author: "Daniel Kaplan"
date: 2018-12-19 
version: 0.2
topics: [zero on y axis, discussion, CO2]
id: crocodile-swim-pot 
---

(ref:crocodile-swim-pot) Exercise in file crocodile-swim-pot

```{r crocodile-swim-pot-default, include = FALSE}
library(NHANES)
library(dplyr)
library(mosaic)
library(mosaicData)
library(ggformula)
MPG_passenger <- 
  MPG %>%
  filter(!is.na(vol_passenger)) 
```

TITLE GOES HERE: The graphic compares carbon-dioxide emissions and fuel use for hybrid and non-hybrid passenger vehicles. 


```{r crocodile-swim-pot-1, echo = FALSE}
MPG_passenger  %>%
  gf_jitter(CO2_year ~ hybrid, data = ., width = 0.1, 
            alpha = 0.5, seed = 101) %>%
  gf_labs(y = "CO2 emissions (kg per year)", x = "Vehicle class", 
          title = "2019 model-year vehicles") %>%
  gf_refine(
      scale_y_continuous(limits = c(1500,NA),
        breaks = c(0, 2000, 4000, 6000),
        sec.axis = sec_axis(name = "Fuel use (gallons per year)", trans = ~ . * 0.113, breaks = c(100 * 0:8))))
```

How much less CO-2- is emitted by the hybrid cars than by a conventional cars? Since CO-2- emission is exactly proportional to fuel burned, there are two vertical axes on the graph.

1. Glancing at the dots in the graphic, quickly form an impression and circle the number of these that seems right.

Circle the right number: *A typical hybrid car emits about ... 10%, 25%, 50%, 75%, 100% ... as much CO-2- as a conventional car.* -A- 50%

2. Now look carefully at the vertical axis and, if necessary, revise your answer in (1).

Revise your answer to (1): *A typical hybrid car emits about ... 10%, 25%, 50%, 75%, 100% ... as much CO-2- as a conventional car.* -A- Note that the vertical axis doesn't include zero. Whenever the interpretation of a graph involves comparing using proportions, zero should be on the y axis. 

For many people, perhaps including you, the answers to (1) and (2) are different. Typically the answer to (1) is smaller than the (correct)  answer to (2).

Figure out a way to revise the graphic so that a quick glance (as in (1)) will suffice to reach a correct conclusion.

<!--answer-start-->
The y-axis doesn't start at zero. Instead, the y-axis is positioned to make the hybrid cars appear to use very little fuel compared to the non-hybrid cars. Certainly, you can read off the value for the hybrid cars from the axis scale, but the *visual impression* is misleading. Here's the same graphic but with the y-axis starting at zero. Insofar as this graphic gives a different impression than the one with a non-zero start to y, you can see why that graph is misleading. 

```{r crocodile-swim-pot-2, echo = FALSE}
MPG_passenger  %>%
  gf_jitter(CO2_year ~ hybrid, data = ., width = 0.1, 
            alpha = 0.5, seed = 101) %>%
  gf_labs(y = "CO2 emissions (kg per year)", x = "Vehicle class", 
          title = "2019 model-year vehicles. Y axis includes zero.") %>%
  gf_refine(
      scale_y_continuous(limits = c(0, NA),
        breaks = c(0, 2000, 4000, 6000),
        sec.axis = sec_axis(name = "Fuel use (gallons per year)", trans = ~ . * 0.113, breaks = c(100 * 0:8))))
```


In general, in situations where a *proportional* comparison is meaningful, the y-axis should include zero. Here, for instance, it's meaningful to say, "Hybrid cars use about two-thirds as much fuel as non-hybrids."

<!--answer-end-->
